LaMachine: A meta-distribution for NLP software

### 2019-02-01 docs/lamachine_clarin2018.tex
[paper] removed singularity bullet point and merged it into a remark, added LXD

\begin{enumerate}
    \item \textbf{Local installation} -- This installs the bulk of LaMachine in a separate local virtual environment (a seperate
        directory\footnote{Python users should know we just use \texttt{virtualenv} for this, with some
        additions of our own}) that has to be explicitly activated to be used. This also allows for multiple different installations
        of LaMachine on the same host system (e.g. for different users or with different software configurations).
        This local installation still actively relies on various global dependencies that are available through the
        package manager of your distribution.
    \item \textbf{Global installation} -- This flavour is used for a host that is fully dedicated to LaMachine. Everything will be
        installed globally so there is only one installation possible, multiple users will all make use of the same
        installation. Unlike the local installation, we do not make use of a Python Virtual Environment in this flavour.
    \item \textbf{Docker container} -- Installs LaMachine in a container. Containerisation separates the entire run-time
        environment from the host system, only the Linux kernel is shared. It is a lighter option than full
        virtualisation. \footnote{Note that Docker on other platforms such as Windows and macOS does do use full
        virtualisation.}
    \item \textbf{Singularity container} -- Another form of containerisation with more focus on security\footnote{reduced
        privilege escalation}, making it more suitable than Docker for deployment on computing clusters. This flavour is still under development.
    \item \textbf{Virtual Machine} --- Installs LaMachine as a virtual machine, i.e. through full virtualisation. This allows
        deployment of LaMachine on hosts which would otherwise not support it, such as Windows. Virtualisation for
        LaMachine is achieved through Vagrant and VirtualBox\footnote{\url{https://vagrant.org}, \url{https://www.virtualbox.org}}.
    \item \textbf{Remote provisioning} -- Installs LaMachine on a remote dedicated server. This option is most suited for
        hosting centres and directly uses Ansible's remote provisioning abilities.
\end{enumerate}

@@

\section{Comparison to alternative distributions}
\label{sec:comparisons}

>>>>

\begin{enumerate}
    \item \textbf{Local installation} -- This installs the bulk of LaMachine in a separate local virtual environment (a seperate
        directory\footnote{Python users should know we just use \texttt{virtualenv} for this, with some
        additions of our own}) that has to be explicitly activated to be used. This also allows for multiple different installations
        of LaMachine on the same host system (e.g. for different users or with different software configurations).
        This local installation still actively relies on various global dependencies that are available through the
        package manager of your distribution.
    \item \textbf{Global installation} -- This flavour is used for a host that is fully dedicated to LaMachine. Everything will be
        installed globally so there is only one installation possible, multiple users will all make use of the same
        installation. Unlike the local installation, we do not make use of a Python Virtual Environment in this flavour.
    \item \textbf{Docker container} -- Installs LaMachine in a container. Containerisation separates the entire run-time
        environment from the host system, only the Linux kernel is shared. It is a lighter option than full
        virtualisation\footnote{Note that Docker on other platforms such as Windows and macOS does do use full
        virtualisation.}.  Support for two other forms of containerisation, i.e. Singularity\footnote{\url{https://www.sylabs.io/singularity/}} and
            LXC/LXD\footnote{\url{https://linuxcontainers.org}}, are currently under development.
    \item \textbf{Virtual Machine} --- Installs LaMachine as a virtual machine, i.e. through full virtualisation. This allows
        deployment of LaMachine on hosts which would otherwise not support it, such as Windows. Virtualisation for
        LaMachine is achieved through Vagrant and VirtualBox\footnote{\url{https://vagrant.org}, \url{https://www.virtualbox.org}}.
    \item \textbf{Remote provisioning} -- Installs LaMachine on a remote dedicated server. This option is most suited for
        hosting centres and directly uses Ansible's remote provisioning abilities.
\end{enumerate}

@@

\section{Comparison to alternative distributions}\label{sec:comparison}
